On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-07 MS.tex
Changes some sentences in the result part to better fit with the cover letter

For wood density, maximum height, and seed mass, correlations with relative growth rate were also consistent with expectations but our ability to test all hypotheses was at times limited due to low sample size. Indeed, while meta-analysis is possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).

@@

@@

As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero). However, the correlations between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig. \ref{fig:fig3}c). Again we could not distinguish between these alternatives. But unlike maximum height, the number of coefficients reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficients reported rather than to a much smaller numbers of replicates.

>>>>

For wood density and seed mass the available results are consistent with expectation from theory but it would be desirable to have substantially more data. Indeed, while meta-analysis is possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).

@@

As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero). However, the correlations between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig. \ref{fig:fig3}c). Again we could not distinguish between these alternatives. But the number of coefficients reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficients reported rather than to a much smaller numbers of replicates.

For maximum height and assimilation rates, correlations with relative growth rate were also consistent with expectations but our ability to test all hypotheses was at times limited due to low or no sample size.

@@
